\LARGE \bf The Battle for Filter Supremacy: A Comparative Study of the Multi-State Constraint Kalman Filter and the Sliding Window Filter

### 2015-03-05 Report/project_report.tex
Another spacing fix

For both tightly coupled and loosely coupled VINS, a popular choice of estimator is the Extended Kalman filter (EKF) or one of its variants \cite{Huster:2002:OC, You:2001:VR, Kottas:2013:RSS, Kim:2007:RSS, Mourikis:2007:ICRA}, though methods also exist that employ unscented Kalman filters \cite{Ebcin:2007:ION}, particle filters \cite{Fox:1999:JAIR, Pupilli:2005:BMVC}, or batch optimization methods\cite{Triggs:2000va,Strelow:2004:IJR}.

@@

Furthermore, EKF-based VINS are inconsistent, that is, the state uncertainties are underestimated.
Li and Mourikis \cite{Li:2013coa} showed that the Jacobians in the linearized model of a VINS have different observability properties than the actual nonlinear system, which reduces the reliability of such estimators.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Multi-State Constraint Kalman Filter} \label{sec:MSCKF}
The Multi-State Constraint Kalman Filter (MSCKF) \cite{Mourikis:2006:TechReport,Mourikis:2007:ICRA} can be thought of as a hybrid of EKF-SLAM and the SWF.
The key idea of the MSCKF is to maintain a variable window of vehicle poses and to simultaneously update each pose in the window using batch-optimized estimates of features that are visible across the entire window.
This update step typically occurs when a tracked feature goes out of view of the camera, but it may also be triggered if the length of a feature track exceeds a preset threshold.
Except where otherwise noted (i.e., \ref{sec:state_parametrization} and \ref{sec:imu_prop}), we implemented the MSCKF as presented in \cite{Mourikis:2006:TechReport, Mourikis:2007:ICRA}.

>>>>

For both tightly coupled and loosely coupled VINS, a popular estimator is the Extended Kalman filter (EKF) or one of its variants \cite{Huster:2002:OC, You:2001:VR, Kottas:2013:RSS, Kim:2007:RSS, Mourikis:2007:ICRA}, though methods also exist that employ unscented Kalman filters \cite{Ebcin:2007:ION}, particle filters \cite{Fox:1999:JAIR, Pupilli:2005:BMVC}, or batch optimization methods\cite{Triggs:2000va,Strelow:2004:IJR}.

@@

Furthermore, EKF-based VINS are inconsistent, that is, the state uncertainties are underestimated.
Li and Mourikis \cite{Li:2013coa} showed that the Jacobians in the linearized model of a VINS have different observability properties than the actual nonlinear system, reducing the reliability of such estimators.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Multi-State Constraint Kalman Filter} \label{sec:MSCKF}
The Multi-State Constraint Kalman Filter (MSCKF) \cite{Mourikis:2006:TechReport,Mourikis:2007:ICRA} can be thought of as a hybrid of EKF-SLAM and the SWF.
The key idea of the MSCKF is to maintain a variable window of vehicle poses and to simultaneously update each pose in the window using batch-optimized estimates of features that are visible across the entire window.
This update step typically occurs when a tracked feature goes out of view of the camera, but it may also be triggered if the length of a feature track exceeds a preset threshold.
Except where otherwise noted (i.e., state parametrization in \ref{sec:state_parametrization} and integration method in \ref{sec:imu_prop}), we implemented the MSCKF as presented in \cite{Mourikis:2006:TechReport, Mourikis:2007:ICRA}.
